Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-01-20 paper.tex
adding Hossam as co-author (I'll add his contributions later)

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo, A.M. Mora, J.J. Merelo, P. Garc\'{\i}a-S\'anchez, \\ A.J. Fern\'andez-Ares, M.G. Arenas, P. de las Cuevas
}
\institute{Department of Computer Architecture and Computer Technology.\\
CITIC-ETSIIT. University of Granada (Spain) \\
           e-mail: {\tt pacv@ugr.es}}

>>>>

%%%%%%%%%%%%%%%% autores %%%%%%%%%%%%%%%
\author {
P.A. Castillo$^1$, A.M. Mora$^1$, J.J. Merelo$^1$, H. Fariss$^2$, \\ P. Garc\'{\i}a-S\'anchez$^1$, A.J. Fern\'andez-Ares$^1$, M.G. Arenas$^1$, P. de las Cuevas$^1$
}
\institute{
$^1$Department of Computer Architecture and Computer Technology. CITIC. University of Granada (Spain)\\
$^2$Business Information Technology Department. King Abdullah II School for Information Technology. The University of Jordan. Amman (Jordan)\\
           e-mail: {\tt pacv@ugr.es}
}
